### 2016-09-21 doc/manuscript.Rmd
Moved inline chunk up, edited/dev methods section

@@

The primary outcome variables for this analysis were 1/HOMA-IR, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA as mole percent
(mol%) of the total fraction and as concentration (nmol/mL). Clinically-measured
TAG is also included as a primary predictor to serve as a comparison against the
TAGFA composition. A limitation with the clinically-measured TAG is that it was
only quantified on a portion of the 6-year visit (n = ~120 {{ find true number
}}). Pearson correlation coefficients were computed to assess the relationships
of individual TAGFA with other continuous variables.

Generalized estimating equation (GEE) models [@Zeger1986a] were used in the
primary analysis to determine the longitudinal associations between the outcome
variables and the predictor variables. An auto-regressive of order 1 (AR1) 
correlation matrix was chosen for the GEE models as it had the best model fit
and given the longitudinal design, though other matrices (eg. exchangeable) had
similar fit (data not shown). GEE is well suited to longitudinal cohort studies
given it's capacity to handle missed visits. The predictor variables and
continuous covariates were scaled (mean centered and standardized). The TAGFA
variables were classified as *time-independent* (held constant) as they were
measured only at the baseline visit, while the outcome variables and covariates
were set as *time-dependent*. No imputation was conducted on missing values.

Covariates were selected based on previous studies, from directed acyclic graph 
[@Greenland1999a] recommendations, and from quasi-likelihood information criterion 
(QIC) {{citation?}}. `r cite_st('qic')` shows the covariates compared using QIC. While the
final GEE model selected as best fitting differed between insulin sensitivity
and beta-cell function measures, the differences in QIC values were less than
10 between the models, suggesting similar fit. As such, we selected the model
that had the fewest covariates and that had similar fit between the outcome
measures ({{##}}). The final GEE model was adjusted for {{covariates}}. After scaling,
log-transforming, and exponentiating, the GEE estimates are
interpreted as an expected percent difference in the outcome variable for every 
standard deviation (SD) increase in the predictor variable given the covariates 
are held constant. Lastly for the GEE models, we tested for an interaction with
sex, ethnicity, or time by the predictor term for each outcome variable.

@@

The number of components to extract from PLS was determined by 10-fold CV.

Dataset was split into a training set and a testing set to determine the
predictability of the given PLS model. Final results presented use the full dataset.a

@@

```{r inline}
dys <- project_data %>% 
    prep_dys_data() %>% 
    calc_convert_dys()

@@

>>>>

```{r inline}
n_tag <- project_data %>% 
    dplyr::filter(VN == 2) %>% 
    dplyr::select(TAG) %>% 
    stats::na.omit() %>% 
    nrow()

dys <- project_data %>% 
    prep_dys_data() %>% 
    calc_convert_dys()

@@

The primary outcome variables for this analysis were 1/HOMA-IR, ISI, IGI/IR, and
ISSI-2, which were log-transformed for the statistical modeling. The primary
predictor variables for this analysis were 22 individual TAGFA as mole percent
(mol%) of the total fraction and as concentration (nmol/mL). Clinically-measured
TAG is also included as a primary predictor to serve as a comparison against the
TAGFA composition. A limitation with the clinically-measured TAG is that it was
only quantified on a portion of the participants at the 6-year visit (n = `r n_tag`).
Pearson correlation coefficients were computed to assess the relationships of
individual TAGFA with other continuous variables.

Generalized estimating equation (GEE) models [@Zeger1986a] were used in the
primary analysis to determine the longitudinal associations between the outcome
variables and the predictor variables. Given the longitudinal design, an
auto-regressive of order 1 (AR1) working correlation matrix was chosen for the GEE
models as it had the best model fit when assessed using quasi-likelihood
information criteria (QIC), though other matrices (eg. exchangeable)
had similar fit (data not shown). GEE is well suited to longitudinal cohort 
studies given it's capacity to handle missed visits. The predictor variables and
continuous covariates were scaled (mean-centered and standardized). The TAGFA,
total NEFA, sex, ethnicity, and baseline age were classified as 
*time-independent* (held constant) as they were measured only at the baseline 
visit or do not change throughout the study, while the outcome variables and 
remaining covariates were set as *time-dependent*. No imputation was conducted 
on missing values.

Covariates were selected based on the previous literature, from directed acyclic
graph [@Greenland1999a] recommendations (see `r cite_st('dag')`), and from 
QIC {{citation?}}. `r cite_st('qic')` shows the covariates compared using QIC.
While the final GEE model selected as best fitting differed between insulin
sensitivity and beta-cell function measures, the differences in QIC values were
less than 10 between the models, suggesting similar fit. As such, we selected
the model that had the fewest covariates and that had similar fit between the
outcome measures ({{##}}). The final GEE model was adjusted for {{covariates}}.
After scaling, log-transforming, and exponentiating, the GEE estimates are 
interpreted as an expected percent difference in the outcome variable for every 
standard deviation (SD) increase in the predictor variable given the covariates 
are held constant. Lastly for the GEE models, we tested for an interaction with 
sex, ethnicity, or time by the predictor term for each outcome variable.

@@

@@

@@

The number of components to extract from PLS was determined by 10-fold CV.
Dataset was split into a training set and a testing set to determine the
predictability of the given PLS model. Final results presented use the full dataset.a
